---
title: "Lab 5"
author: "Patrick Pelegri-O'Day"
date: "10/25/2021"
output: 
  html_document: 
    theme: spacelab
    toc: yes
    code_folding: hide # important: this allows your code to be hidden by default
---
## Overview

Overview text

## Setup
```{r setup, include=TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(effsize)
```

## Part 1: Confidence intervals

In this section, we'll use the `t.test()` function to calculate confidence intervals.

### Example 1

Create a single mock sample containing a number of values then learn to use  `t.test()` to return confidence intervals, and learn about in-line code referencing so our text becomes more reproducible too.

```{r}
# Create a mock sample

otter_lengths <- c(42, 23, 19, 49, 39, 28, 30)

# Find the confidence interval:
otter_ci <- t.test(otter_lengths) # returns one-sample t-test. default null hypothesis is that true mean = 0

# 95% confidence interval: if we took multiple samples of pop, we'd expect that 95% of the confidence intervals would contain the population mean

# Find the standard deviation
otter_sd <- sd(otter_lengths)
```

Mean otter length is 32.8 inches, $\pm$ 10.8 (mean $\pm$, n = 7) with a 95% confidence interval of [22.8 ,42.9)]

#### Now, using in-line referencing

Mean otter length is `r round(otter_ci$estimate, 1)` inches. (Hover over the value and click cmnd-return to see value.) (`round(value, significant figure)` rounds a value to the specified significant figure)
