---
title: "Lab 5"
author: "Patrick Pelegri-O'Day"
date: "10/25/2021"
output: 
  html_document: 
    theme: spacelab
    toc: yes
    code_folding: hide # important: this allows your code to be hidden by default
---
## Overview

Overview text

## Setup
```{r setup, include=TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(effsize)
```

## Part 1: Confidence intervals

In this section, we'll use the `t.test()` function to calculate confidence intervals.

### Example 1

Create a single mock sample containing a number of values then learn to use  `t.test()` to return confidence intervals, and learn about in-line code referencing so our text becomes more reproducible too.

```{r}
# Create a mock sample

otter_lengths <- c(42, 23, 19, 49, 39, 28, 30)

# Find the confidence interval:
otter_ci <- t.test(otter_lengths) # returns one-sample t-test. default null hypothesis is that true mean = 0

# 95% confidence interval: if we took multiple samples of pop, we'd expect that 95% of the confidence intervals would contain the population mean

# Find the standard deviation
otter_sd <- sd(otter_lengths)
```

Mean otter length is 32.9 inches, $\pm$ 10.8 (mean $\pm$, n = 7) with a 95% confidence interval of [22.8 ,42.9)]

#### Now, using in-line referencing

Mean otter length is `r round(otter_ci$estimate, 1)` inches with a 95% confience interval of [`r round(otter_ci$conf.int[1], 1)`, `r round(otter_ci$conf.int[2], 1)`] inches

- Hover over the value and click cmnd-return to see value.
- `round(value, significant figure)` rounds a value to the specified significant figure
- the generic version of in-line referencing is objectname$valuename
- if the value you are calling is a vector and you want to reference a specific value within that vector, then the syntax is `objectname$valuename[#]` where `#` refers to the position in that vector/list

## Part 2: Two-sample t-tests

### Example 1

Make two mock samples, and ask the question: do we have sufficient evidence to make us reject the null hypothesis that these samples were drawn from populations with the same mean?

```{r}
# Make my mock samples
oak_trees <- c(20, 19, 24, 28, 30, 35, 12, 32)
  
pine_trees <- c( 39, 41, 35, 22, 19, 37, 18)

# Two-sample t-test
trees_t <- t.test(oak_trees, pine_trees)

# Null hypothesis: mean heights are the same
# i.e.: Trees are drawn from populations with the same mean height
```
Meaning of the p-value is that, if these are drawn from populations from the same mean, there is a 29% chance that two means are at least as different as 1.1 feet

The mean heights of oak and pine trees were (X +- Y) and (X +- Y), respectively, and the difference was not significant (t(`r trees_t$parameter`) = `r trees_t$statistic`, p = `r trees_t$p.value`)
- Format with which we summarize results of t-test: "t(df) = t-statistic, p = p-value"

## Part 3: Another t-test with cars data

Using the `mpg` dataset

### Take a look at the data

```{r}
compact_suv <- mpg %>% 
  filter(class %in% c("compact", "suv"))

# Check for remaining levels
unique(compact_suv$class)
```

Create a histogram of city gas mileage (city) faceted by class starting from compact_suv

```{r}
ggplot(data = compact_suv, aes(x = cty)) +
  geom_histogram(bins = 10) +
  facet_wrap(~class)

ggplot(data = compact_suv, aes(sample = cty)) +
  geom_qq() + 
  facet_wrap(~class) +
  geom_qq_line()
```

Find some summary statistics for each group
```{r}
car_stats <- compact_suv %>% 
  group_by(class) %>% 
  summarize(
    mean_city = round(mean(cty), 2), # you can round here, but it's better to round in the data visualization. here it's ok to round because this value is only being used for visualization, not for further calculations 
    sd_city = round(sd(cty), 2),
    sample_size = n()
  )

car_stats
```

The t.test() function REALLY wants vectors of things. So to run a t-test we want to pull out vectors from our data frame. Use the `pull()` function to pull out a vector from a data frame

```{r}
compact_sample <- compact_suv %>% 
  filter(class == "compact") %>% 
  pull(cty)

# Do the same thing to get a vector of city gas mileages for SUVs

suv_sample <- compact_suv %>% 
  filter(class == "suv") %>% 
  pull(cty)
```

H0: Mean city gas mileages for SUVs and compact cars are the same

```{r}
t.test(compact_sample, suv_sample)
```

