---
title: "Lab 5"
author: "Patrick Pelegri-O'Day"
date: "10/25/2021"
output: 
  html_document: 
    theme: spacelab
    toc: yes
    code_folding: hide # important: this allows your code to be hidden by default
---
## Overview

Overview text

## Setup
```{r setup, include=TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(effsize)
```

## Part 1: Confidence intervals

In this section, we'll use the `t.test()` function to calculate confidence intervals.

### Example 1

Create a single mock sample containing a number of values then learn to use  `t.test()` to return confidence intervals, and learn about in-line code referencing so our text becomes more reproducible too.

```{r}
# Create a mock sample

otter_lengths <- c(42, 23, 19, 49, 39, 28, 30)

# Find the confidence interval:
otter_ci <- t.test(otter_lengths) # returns one-sample t-test. default null hypothesis is that true mean = 0

# 95% confidence interval: if we took multiple samples of pop, we'd expect that 95% of the confidence intervals would contain the population mean

# Find the standard deviation
otter_sd <- sd(otter_lengths)
```

Mean otter length is 32.9 inches, $\pm$ 10.8 (mean $\pm$, n = 7) with a 95% confidence interval of [22.8 ,42.9)]

#### Now, using in-line referencing

Mean otter length is `r round(otter_ci$estimate, 1)` inches with a 95% confience interval of [`r round(otter_ci$conf.int[1], 1)`, `r round(otter_ci$conf.int[2], 1)`] inches

- Hover over the value and click cmnd-return to see value.
- `round(value, significant figure)` rounds a value to the specified significant figure
- the generic version of in-line referencing is objectname$valuename
- if the value you are calling is a vector and you want to reference a specific value within that vector, then the syntax is `objectname$valuename[#]` where `#` refers to the position in that vector/list

## Part 2: Two-sample t-tests

### Example 1

Make two mock samples, and ask the question: do we have sufficient evidence to make us reject the null hypothesis that these samples were drawn from populations with the same mean?

```{r}
# Make my mock samples
oak_trees <- c(20, 19, 24, 28, 30, 35, 12, 32)
  
pine_trees <- c( 39, 41, 35, 22, 19, 37, 18)

# Two-sample t-test
trees_t <- t.test(oak_trees, pine_trees)

# Null hypothesis: mean heights are the same
# i.e.: Trees are drawn from populations with the same mean height
```
Meaning of the p-value is that, if these are drawn from populations from the same mean, there is a 29% chance that two means are at least as different as 1.1 feet

The mean heights of oak and pine trees were (X +- Y) and (X +- Y), respectively, and the difference was not significant (t(`r trees_t$parameter`) = `r trees_t$statistic`, p = `r trees_t$p.value`)
- Format with which we summarize results of t-test: "t(df) = t-statistic, p = p-value"
